Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-06 Latex/tex/pr.tex
add latex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

@@

Assume that for simplicity, each VM is mapped to one virtual network function (VNF). Each VNF requires

@@

\subsection{Problem Formulation}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

@@

We define a new parameter which indicates mean delay of each slice
D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s

@@

Assume each VM is mapped to one virtual network function (VNF) for simplicity. Each VNF requires

@@

\begin{equation*}
\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \}
\end{equation*}
\subsection{Problem Statement}
One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as sum-rate to sum-power as follow
\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},
Assume the power consumption of baseband processing at each data center that is mapped to VMs of a slice is depicted as
$\phi$. So the total power can be represented as  
\begin{equation*}
\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}x_{s,d}\phi
\end{equation*} 
Where, $x_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\
In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power with the presence of constraints which is written as follow, 
\begin{subequations}
\begin{alignat}{4}
\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{X} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{X})} \\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
&D_{s} \leq D_{s}^{th}  &&\quad \forall s, \\
& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 
\end{alignat}
\label{constraints}
\end{subequations}
Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{X} =[x_{s,d}]  \forall s , \forall d $.
The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem. The First and main problem is
\begin{subequations}
\begin{alignat}{4}
\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
&D_{s} \leq D_{s}^{th}  &&\quad \forall s
\end{alignat}
\label{constraints1}
\end{subequations}
and the second problem is 
\begin{subequations}
\begin{alignat}{4}
\min\limits_{\boldsymbol{X} }   \quad &   \phi_{tot}(\boldsymbol{X})\\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 
\end{alignat}
\label{constraints2}
\end{subequations}
\subsection{Proposed Method}
In this subsection, the proposed method is applied to solve the optimization problem. 
\subsubsection{First Sub-Problem}
In this part, we want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 
two different part that iteratively solve. 
Firstly, we want to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1}. This part of problem is solved in two different method. The first method is using MOSEK and second method is a heuristic method.
The details of heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
\begin{algorithm}
\caption{Mapping Slice to Service}\label{alg}
\begin{algorithmic}[1]
\State Sort Services according to their priority and the number of Users in the services and their requirements.
\State Sort Slices according to the number of PRBs and number of RRHs and VMs  and their max of Capacities of resources. 
\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
\State Set the iteration index $i = 1$ and begin the iteration (Outer
Loop).
\For {$ 1\leq i \leq  Imax$}
\State Solve the resource allocation problem with $\eta^{(i)}$ (Inner Loop);
\State Obtain $P^{(i)}, R_{total}^{(i)}, P_{RRH}^{(i)}$
\If {$ R_{total}(\boldsymbol{P}^{(i)}) - \eta^{(i)} P_{RRH}(\boldsymbol{P}^{(i)}) < \epsilon_{\eta} $} 
\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
\State break;
\Else
\State Set $\eta^{(i)}= \frac{R_{total}(\boldsymbol{P}^{(i))}}{P_{RRH}(\boldsymbol{P}^{(i))}}$ and $i= i+1$;
\EndIf 
\State \textbf{end if}
\EndFor 
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
